---
title: "README"
author: "Dian"
date: "18 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Tutorial
This tutorial will serve as a practise round for our project. Completing this tutorial will give us the necessary tools to produce our paper in texevier when we do our project, as well as aid us in future endevours.

First lets load the data and required packages. I did this in seperate scripts to avoid errors and for a neater work space.
```{r, include=FALSE}
library(rmsfuns)
load_pkg(c("tidyverse", "devtools", "rugarch", "forecast", "tbl2xts", 
           "lubridate", "PerformanceAnalytics", "ggthemes", "xtable", "parallel", "robustbase"))

dailydata <- read_csv("https://raw.githubusercontent.com/Nicktz/ExDat/master/extdata/findata.csv", 
                      col_types = cols(.default = "d", Date = "D"))

```

The next step is to put the data in tidy format
```{r Making the data tidy}
tidy <- dailydata %>% 
  gather(key = Stocks, value = values, contains("close"))

```

Using the tidy data, lets calculate and create a new column for returns
```{r}
return_stocks <- tidy %>% 
  group_by(Stocks) %>% 
  mutate(Ret_stocks = values/lag(values) -1) %>% 
  mutate(LogRet_stocks = log(1 + Ret_stocks/100)*100)
```

Now that we have the returns, let's calculate the moments for the two periods. 
```{r}
#Period 1

Moments_period1 <- return_stocks %>% filter(Date >= ymd(20060518) & Date < ymd(20071231)) %>% 
  group_by(Stocks) %>% 
  summarise(period1_mean = mean(Ret_stocks, na.rm = T),period1_variance = var(Ret_stocks, na.rm = T)) %>% 
  tbl_df()


#Now period 2

Moments_period2 <- return_stocks %>% filter(Date >= ymd(20100101) & Date < ymd(20121231)) %>% 
  group_by(Stocks) %>% 
  summarise(period1_mean = mean(Ret_stocks, na.rm = T),period1_variance = var(Ret_stocks, na.rm = T)) %>% 
  tbl_df()
```
This is now put into texevier using xtable, to produce a neat and tidy table.

2006-2008
```{r Table1, results = 'asis'}

library(xtable)

table <- xtable(Moments_period1, caption = "Moments of the stocks for 2006-2008 \\label{tab1}")
  print.xtable(table, 
             floating = TRUE,
             table.placement = 'H', 
             comment = FALSE,
             caption.placement = 'bottom'
             )
```
  
2010-2013
```{r Table2, results = 'asis'}

library(xtable)

table <- xtable(Moments_period2, caption = "Moments of the stocks for 2010-2013 \\label{tab1}")
  print.xtable(table, 
             floating = TRUE,
             table.placement = 'H', 
             comment = FALSE,
             caption.placement = 'bottom'
             )
```

Next we have to include references, using bibtex from google scholar. This was relatively simple. Copying the bibtex from google scholar and pasting it in our ref.bib file, and then simply calling the reference using the shortcut.

The most notable differences between the two periods is the negative mean values in period 1 (2006-2008) for ABSP and NBKP. Additionally, the variance between the two periods differs substantially for every stock except NBKP and RMH. ABSP has the highest variance in returns across both periods, suggesting that it is the most volatile of the stocks [@Texevier \& @Tsay1989]. 

#Question 2: Calculating the full sample correlations between the stocks \label{Question 2: Calculate the full sample correlations between the stocks}

This was relatively simple as well. I have done correlations and cross correlations for my thesis, so I knew what to do here. I changed the size of the table using scalebox, as the table would not fit on the page initially.
```{r Table3, results='asis'}

print.xtable(xtable(cor(dailydata[, c(2,3,4,5,6,7,8)], use = "complete.obs"), caption = "Unconditional Correlations Between Stocks \\label{t}"),
             floating = TRUE,
             table.placement = 'H', 
             scalebox = "0.7",
             comment = FALSE,
             caption.placement = 'bottom'
             )
```
# Question 3: Plot the univariate GARCH ht processes for each of the series 

First we need to make the data wide (spread it)
```{r}
Data_wide <- 
  subset(return_stocks, select = -c(values, Ret_stocks)) %>% 
  spread(key = Stocks, value = LogRet_stocks) %>% 
  tbl_xts()

Data_wide <- na.omit(Data_wide)
```
Note that "Data_wide"" is created which has the log returns of all the stocks. This data has been spread, after the log returns were calclulated for each stocks from the dailydata.

Next is the GARCH calculations, to produce univariate GARCH ht processes for each of the series. This was not easy. It took some time, but finally got it right. It still produces, "##calculating quantiles" in the pdf which is annoying.

```{r figure1, warning =  FALSE, fig.align = 'center', fig.cap = "GARCH Plot \\label{lit}", fig.ext = 'png'}

###### This was taken straight from practical 6
cl = makePSOCKcluster(10)

# I use the partial method below, otherwise it might take a
# long time to run.
#first we need to create an equally weighted portfolio. We need to use the wide data, so that we can have univariate GARCH processes for EACH series
portfolio_eqw <- Return.portfolio(Data_wide, weight = NULL, geometric = FALSE) 


AC = autoarfima(as.numeric(portfolio_eqw), ar.max = 2, ma.max = 2, 
                criterion = "AIC", method = "partial", arfima = FALSE, include.mean = NULL, 
                distribution.model = "norm", solver = "solnp", cluster = cl)

#show(head(AC$rank.matrix))
#This tells us what the optimal rank is(guides us)

garch11 <- ugarchspec(variance.model = list(model = c("sGARCH", 
                                                      "gjrGARCH", "eGARCH", "fGARCH", "apARCH")[1], garchOrder = c(2,2)), mean.model = list(armaOrder = c(1, 0), include.mean = TRUE), 
                      distribution.model = c("norm", "snorm", "std", "sstd", "ged", 
                                             "sged", "nig", "ghyp", "jsu")[1])


# Now to fit, I use as.matrix and the data - this way the
# plot functions we will use later will work.

garchfit1 = ugarchfit(spec = garch11, data = as.numeric(portfolio_eqw))

# Note it saved a S4 class object - having its own plots and
# functionalities:

class(garchfit1)

```

# Question 4: Plot the cumulative returns series of a portfolio that is equally weighted to each of the stocks - reweighted each year on the last day of June.

Again, this wasn't too difficult. We did calculate cumulative returns in our previous assignment, which helped a lot.
```{r figure2, warning =  FALSE, fig.align = 'center', fig.cap = "Cumulative returns plot- equally weighted \\label{lit}", fig.ext ='png'}

Cumulative_portfolio_eqw <-portfolio_eqw %>% 
  xts_tbl() %>% 
  mutate(portfolio.returns = coalesce(portfolio.returns, 0)) %>% 
  mutate(cumulative_ret = cumprod(1+ portfolio.returns))

ggplot(Cumulative_portfolio_eqw) + 
  geom_line(aes(date,cumulative_ret), color = "Red") +
  theme_bw() + labs(title = "Equally Weighted Portfolio's Cumulative Returns")
```

Unfortunately I was unable to reweight the portfolio on the last day of June each year. I tried using what was provided in practical 5, and I have the intuition behind it. However, there appears to be an error in my code (clearly I am missing something).

As such, this brings an end to my first paper produced in texevier. Excting times ahead!